Predicting sales of newly published books

### 2015-10-16 paper.tex
results section

%
% TODO: explicar los resultados obtenidos en la selección de variables (1) con el SOM (2) con los métodos de selecc. vars.
%

@@

% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
% -

@@

Proposed methods (M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialization seed for each run.

>>>>

@@

%
% TODO: explicar los resultados obtenidos en la selección de variables: 
%  (1) con el SOM, (2) con los métodos de selecc. vars.
%
% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
To do so, in a first stage, the feature selection process has been carried out 
using both the CfsSubsetEval \cite{Hall1998} (a correlation-based feature subset 
evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
adaptation of relief for attribute estimation) evaluation methods.

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print_run, num_reprints, tot_points_sale, tot_points_sale_1st_year, reprints, distrib_novelty, weeks_sale, total_sales}.

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the CfsSubsetEval feature selection method, the following variables have 
been selected: \emph{num_reprints, tot_points_sale, print_run, total_sales}.

% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
% seleccionaron las variables más adecuadas.
Then, an exhaustive analisys of the SOM results was carried out in order to 
determine the best variables to be considered to buid the forecasting model.

\textbf{ TODO: add the SOM analisys }

Once the different reduced datasets have been obtained, proposed methods 
(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialization seed for each run.

@@
